SNARL:\\Simulating Known Actors with Machine Learning

### 2017-05-15 tex/paper/paper.tex
Fix typo.

We present an exploration into the pitfalls of relying on input-delay-based biometric data as a second factor for authentication, using \texttt{punchTimeAuth} as our standard for comparison. We show that the model introduces a prohibitively high number false negatives when exposed to real-world usage. Furthermore, we present several adversarial models which can successfully impersonate a user typing their password, trained on background typing data that need not include the password itself. In order to collect this data, we built two collection mediums: a Google Documents look-alike and an extension for Google Chrome. We collect which keys are pressed, the length of time each is held for, and the delay between each pair of keys. Finally, we present a novel neural model for attempting to distinguish users based on the information we collect, along with some conclusions and observations about this source of data as a second factor for security.

@@

We implemented a small client-side library in JavaScript which listens for the \texttt{KeyDown} and \texttt{KeyUp} DOM events emitted from the textbox, so as to record the length of time each key is held for and the delay between key presses, as well as the actual characters being typed. This data is stored in a local buffer and is periodically uploaded to our servers, where a a Flask app records the logged objects to a MongoDB instance, tagged with a unique identifier for the user in question.

>>>>

We present an exploration into the pitfalls of relying on input-delay-based biometric data as a second factor for authentication, using \texttt{punchTimeAuth} as our standard for comparison. We show that the model introduces a prohibitively high number of false negatives when exposed to real-world usage. Furthermore, we present several adversarial models which can successfully impersonate a user typing their password, trained on background typing data that need not include the password itself. In order to collect this data, we built two collection mediums: a Google Documents look-alike and an extension for Google Chrome. We collect which keys are pressed, the length of time each is held for, and the delay between each pair of keys. Finally, we present a novel neural model for attempting to distinguish users based on the information we collect, along with some conclusions and observations about this source of data as a second factor for security.

@@

We implemented a small client-side library in JavaScript which listens for the \texttt{KeyDown} and \texttt{KeyUp} DOM events emitted from the textbox, so as to record the length of time each key is held for and the delay between key presses, as well as the actual characters being typed. This data is stored in a local buffer and is periodically uploaded to our servers, where a Flask app records the logged objects to a MongoDB instance, tagged with a unique identifier for the user in question.
